Efficient, Robust and Exact Boolean Operations on N Triangular Mesh Primitives

### 2016-08-01 summary.tex
done with the first round

Because $v_{x'}(t_i)$ can be arbitrarily close to $v_b^2(t_i)$, if $\lambda(v_b^2(t_i), P_j) = in | out$, $\lambda(v_{x'}(t_i), P_j)=\lambda(v_b^2(t_i), P_j)$ holds for the continuity of space. If $\lambda(v_b^2(t_i), P_j) = on$, we divide the proof of $\lambda(v_{x'}(t_i), P_j)=on$ into two parts. If $C_{P_h \backslash P_j}$ is face neighboring type, $\boldsymbol{D}(C_{P_h \backslash P_j})$

>>>>

Given $v_{x'}(t_i)$ can be arbitrarily close to $v_b^2(t_i)$, if $\lambda(v_b^2(t_i), P_j) = in | out$, the equality holds because of the continuity of space. If $\lambda(v_b^2(t_i), P_j) = on$, we divide the proof of equality into two parts according to the type of intersection context. If $C_{P_h \backslash P_j}$ is face neighboring type, $\boldsymbol{D}(C_{P_h \backslash P_j})$ is a single face, say, $t_0^c$. We have already know that the other two corners $v_{b*}^{0}(t_i)$ and $v_{b*}^{1}(t_i)$ are on $s_0$. Since $\lambda(v_b^2(t_i), P_j) = on$, we know $v_b^2(t_i)$ is on $t_0^c$, too. There comes the conclusion that the whole triangle $t_i$ is coplanar with $t_0^c$. Therefore, $v_{x'}(t_i)$ is on $t_0^c$ and $\lambda(v_{x'}(t_i), P_j) = on$, too. On the other hand, if $C_{P_h \backslash P_j}$ is edge neighboring type, $\boldsymbol{D}(C_{P_h \backslash P_j})$ are two neighboring faces (denoted as $t_1^c, t_2^c$). We know that both $v_{b*}^{0}(t_i)$ and $v_{b*}^{1}(t_i)$ are on the shared edge $e(v_{b*}^{0}(t_i), v_{b*}^{1}(t_i))$. It means both vertices are on both $t_1^c$ and $t_2^c$. Using the same deduction of the first condition, we can conclude $\lambda(v_{x'}(t_i), P_j) = on$ whenever $\lambda(v_b^2(t_i), P_j) = on$.
